\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Ethan Havemann} \\ \vspace{1pt}
    \small (972) 795-4019 $|$ \href{mailto:ethavemann@gmail.com}{\underline{ethavemann@gmail.com}} $|$ 
    \href{https://linkedin.com/in/echavemann}{\underline{linkedin.com/in/echavemann}} $|$
    \href{https://github.com/echavemann}{\underline{github.com/echavemann}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northwestern University}{Evanston, IL}
      {B.S. in Computer Engineering}{Expected June 2025}
      \resumeItemListStart
          \resumeItem{Minor in Mathematics; Residential Assistant ('22-'25); GPA: 3.85/4.00; Major GPA: 4.00/4.00.}
          \resumeItem{Relevant Coursework: Operating Systems, Distributed Systems, (Advanced) Computer Architecture, Compiler Construction, Computer Networks, Data Structures, Statistical Learning, Stochastic Processes }
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Optiver}{June 2024 -- August 2024}
      {Software Engineering Intern - High Frequency Trading Execution}{Austin, TX}
    \resumeItemListStart
    \resumeItem{Rebuilt simulation environment for new auto-trader in C++, replaying all data feeds and supporting systems.}
    \resumeItem{Designed and implemented tooling to allow simulation without requiring quantity limited FPGAs, while maintaining competitive accuracy with production environment and improved visibility into trading state.}
    \resumeItem{Designed and implemented out of band latency analysis tooling to enable reproducible, consistent, and accurate performance profiling and optimization.}
    \resumeItemListEnd
    \resumeSubheading
      {Amazon Web Services (AWS)}{June 2023 -- August 2023}
      {Software Engineering Intern -- People Screening}{Seattle, WA}
     \resumeItemListStart
     \resumeItem{Designed and implemented fully automated screening and case lifecycle management pipeline using Java and AWS.}
     \resumeItem{Built novel system consuming JSON to dynamically create business rules, configured to consume from a prebaked UI for non-technical consumers. Worked extensively with other teams to resolve blockers and interteam issues.}
     \resumeItem{Automated case maintenance actions within the US, removing over 10,000 human interventions per month.}
     \resumeItemListEnd
    \resumeSubheading
      {Amazon}{September 2022 -- December 2022}
      {Software Engineering Intern -- Advertising Data Compute Orchestration Team}{Boulder, CO}
      \resumeItemListStart
        \resumeItem{Refactored existing job runner to allow reporting of metrics as well and make design more extensible, develop automatic monitoring microservice for internal EMR fork, surfacing metrics for 250M+ daily spark jobs.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Acorn Genetics -- Genetic Testing Startup}{May 2022 -- September 2022}
      {Software Engineer Intern}{Evanston, IL}
      \resumeItemListStart
        \resumeItem{Lead on Acorn's SANDY genetic processing library (Python), maintaining feature parity to industry leader.}
      \resumeItemListEnd
        \resumeSubheading
      {Northwestern University}{September 2023 -- Present}
      {Teaching Assistant, Guest Lecturer}{Evanston, IL}
      \resumeItemListStart
        \resumeItem{Teaching Assistant for Computer Science 213 - Intro Computer Systems (Fall 2023, Winter, Spring 2024)}
        \resumeItem{Teaching Assistant for Computer Science 343 - Operating Systems (Fall 2024)}
        \resumeItem{Teaching Assistant + Guest Lecturer for Industrial Engineering 304 - Statistical Learning (Winter, Spring 2024}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Northwestern Financial Technologies Club} $|$ \emph{Founder and President}}{January 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Steer technical and programmatic direction of organization, giving lectures on various relevant topics, overseeing development projects, and providing mentorship and advice for 30+ student developers.}
            \resumeItem{Conceptualized and assisted with infrastructure design and case direction on the Northwestern Trading Contest.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Walkway - EE/CS 499} $|$ \emph{Independent Study}}{March 2022 - Present}
          \resumeItemListStart
            \resumeItem{Graduate Study advised by Professors Ilya Mikhelson and Zhaoran Wang on applied RL in Crypto Futures.}
            \resumeItem{Built in-house research platform, data pipelines, cloud agnostic deployment code, and feature extraction engines.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------HONORS AND AWARDS-----------
\section{Honors and Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{2023 UChicago Trading Contest} $|$ \emph{Team Lead, 3rd Place Market Making, 5th Place Portfolio Optimization}}{}
    \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Python, C, Java, Go, R, Verilog, Typescript, Bash, \LaTeX} \\
     \textbf{Technologies}{: UNIX (RHEL/Rocky, Ubuntu), Cloud Infrastructure, APIs, Concurrency, Data Systems } \\
    \textbf{Developer Tools}{: Git, GitHub + Actions, Jenkins, SSH, Terraform, Ansible, Cloud Platforms, Wireshark, GDB} \\
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
